The dictionary for characters of smooth group schemes

### 2016-03-30 followup.tex
Fixed a conflict :-(

A Yu type is a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$,  olnstructed from the following information, derived from a Yu datum:
\begin{enumerate}
\labitem{Y0}{Y0} a sequence of compact groups $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$;
\labitem{Y1}{Y1} a continuous representation $\rho_0$ of $C^0$;
\labitem{Y2}{Y2} quasicharacters $\varphi^i : C^i \to \CC^\times$, for $i=0, \ldots d$.
\end{enumerate}
%
The representation $\rho_0$ and the quasicharacters $(\varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\rho_i$ of $C^i$, for $i=1, \ldots, d$ such that $\rho_d \otimes \varphi^d = \rho$ as representations of $C^d = C$.
%
Since we will need some facts about this construction in the proof of Theorem~\ref{thm:geotypes}, we review some further detail here.
In Table~\ref{table:notation} we explain how to convert the constructions appearing in this section into the notation of \cite{yu:01a}.

@@

\bibliography{bibliography/Biblio}
% \bib, bibdiv, biblist are defined by the amsrefs package.
%\iffalse

>>>>

A Yu type is a pair $(C,\rho)$, where $C$ is a compact group and $\rho$ is a representation of $C$, constructed from the following information, derived from a Yu datum:
\begin{enumerate}
\labitem{Y0}{Y0} a sequence of compact groups $C^0 \subseteq C^1 \subseteq \cdots \subseteq C^d= C$;
\labitem{Y1}{Y1} a continuous representation $\rho_0$ of $C^0$;
\labitem{Y2}{Y2} quasicharacters $\varphi^i : C^i \to \CC^\times$, for $i=0, \ldots d$.
\end{enumerate}
%
The representation $\rho_0$ and the quasicharacters $(\varphi^0, \ldots , \varphi^d)$ enjoy certain properties which allow Yu to construct representations $\rho_i$ of $C^i$, for $i=1, \ldots, d$ such that $\rho_d \otimes \varphi^d = \rho$ as representations of $C^d = C$.
%
Since we will need some facts about this construction in the proof of Theorem~\ref{thm:geotypes}, we review some further detail here.
In Table~\ref{table:notation} we explain how to convert the constructions appearing in this section into the notation of \cite{yu:01a}.

@@

%\bibliography{bibliography/Biblio}
% \bib, bibdiv, biblist are defined by the amsrefs package.
%\iffalse
